CRUSE to Safe Cycling in Ireland \\\large{An Open Source Methodology to Support Active Travel}

### 2023-09-14 paper.qmd
Fix website

# Uncomment the following line to produce the cover page
author:
  - name: Dr. Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Dr. Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Dr. Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY, UK
abstract: |
  Under the EU Road infrastructure safety management (RISM) directive, the National Road Safety Strategy (RSS), and the Climate Action Plan Transport Infrastructure Ireland (TII) has a remit for road safety and decarbonizing a predominantly road-based network in Ireland.

@@

  As countries, like Ireland, invest in cycling, the number of killed and seriously injured cyclists must reduce too.
  The CRUSE Tool provides estimates of cycling potential and routing for each county in Ireland, and works in both urban and rural settings, to enable monitoring of cycling safety.
  With growth in the E-bike market, the tool will help inform inter-urban and rural networks to support the transfer of trips to sustainable modes for longer journeys.
  The CRUSE Tool methodology and findings are directly relevant to addressing the challenges and opportunities faced by other NRAs.
  The datasets resulting from the project are open access and can be used by both non-experts and professionals.
keywords: 
  - Cycling
  - Open-source
  - Road Safety
  - Active Travel
date: last-modified

format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
---

@@

@@

@@

>>>>

# # Uncomment for formatted version
# format:
#   elsevier-pdf:
#     keep-tex: true
#     journal:
#       name: Journal Name
#       formatting: preprint
#       model: 3p
#       cite-style: super

# Uncomment the following line to produce the cover page
author:
  - name: Dr. Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Dr. Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY, UK
  - name: "Gary O'Tool"
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY, UK
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Dr. Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
abstract: |
  Under the EU Road infrastructure safety management (RISM) directive, the National Road Safety Strategy (RSS), and the Climate Action Plan Transport Infrastructure Ireland (TII) has a remit for road safety and decarbonizing a predominantly road-based network in Ireland.

@@

  As countries, like Ireland, invest in cycling, the number of killed and seriously injured cyclists must reduce too.
  The CRUSE Tool provides estimates of cycling potential and routing for each county in Ireland, and works in both urban and rural settings, to enable monitoring of cycling safety.
  With growth in the E-bike market, the tool will help inform inter-urban and rural networks to support the transfer of trips to sustainable modes for longer journeys.
  The CRUSE Tool methodology and findings are directly relevant to addressing the challenges and opportunities faced by other NRAs.
  The datasets resulting from the project are open access and can be used by both non-experts and professionals.
keywords: 
  - Cycling
  - Open-source
  - Road Safety
  - Active Travel
date: last-modified
---

@@

Mobility hub.

Business cases need evidence.

Como UK.

@@

In this context, TII commissioned the CRUSE project which is...

The rest of paper is structured as follows...

@@

National planning

Regional

Local

### 2023-09-14 paper.tex
Fix website

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={CRUSE to Safe Cycling in Ireland},
  pdfauthor={Dr.~Robin Lovelace; Dr.~Joey Talbot; Eugeni Vidal Tortosa; Hussein Mahfouz; Dan Brennan; Dr.~Suzanne Meade; Elaine Brick; Peter Wright},
  pdfkeywords={Cycling, Open-source, Road Safety, Active Travel},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\author[2]{Dan Brennan%
%
}

\author[2]{Dr.~Suzanne Meade%
%
}

\author[3]{Elaine Brick%
%
}

\author[4]{Peter Wright%
%
}

\affiliation[1]{organization={University of
Leeds},addressline={Institute for Transport Studies, Leeds, LS2 9JT,
United Kingdom},postcodesep={}}
\affiliation[2]{organization={Transport Infrastructure
Ireland},addressline={Parkgate Business Centre, Parkgate Street, Dublin
8, D08 DK10, Ireland},postcodesep={}}
\affiliation[3]{organization={AECOM},addressline={Unit 6, Galway
Technology Park, Parkmore, Galway, Ireland},postcodesep={}}
\affiliation[4]{organization={AECOM},addressline={Winslade House,
Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY,
UK},postcodesep={}}

@@

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, sharp corners, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

@@

Uptake of cycling, the main topic of this paper, should be seen in this
broader context of transport decarbonisation. Although cycling uptake
appears on the surface to only relate to the `shift' part of the ASI
framework, closer consideration of the knock-on impacts of cycling
uptake shows that it can also help avoid unnecessary trips {[}citation
needed, any ideas Hussein?{]} . The rapid uptake of highly efficient
e-bikes can also be seen as an improvement on most electric vehicles,
which are too heavy and expensive to be a sustainable alternative and
could in fact delay the transition away from car dependency {[}citation
needed{]}.

@@

>>>>

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={CRUSE to Safe Cycling in Ireland},
  pdfauthor={Dr.~Robin Lovelace; Dr.~Joey Talbot; Eugeni Vidal Tortosa; Hussein Mahfouz; Elaine Brick; Peter Wright; Gary O'Tool; Dan Brennan; Dr.~Suzanne Meade},
  pdfkeywords={Cycling, Open-source, Road Safety, Active Travel},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\author[2]{Elaine Brick%
%
}

\author[3]{Peter Wright%
%
}

\author[3]{Gary O'Tool%
%
}

\author[4]{Dan Brennan%
%
}

\author[4]{Dr.~Suzanne Meade%
%
}

\affiliation[1]{organization={University of
Leeds},addressline={Institute for Transport Studies, Leeds, LS2 9JT,
United Kingdom},postcodesep={}}
\affiliation[2]{organization={AECOM},addressline={Unit 6, Galway
Technology Park, Parkmore, Galway, Ireland},postcodesep={}}
\affiliation[3]{organization={AECOM},addressline={Winslade House,
Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY,
UK},postcodesep={}}
\affiliation[4]{organization={Transport Infrastructure
Ireland},addressline={Parkgate Business Centre, Parkgate Street, Dublin
8, D08 DK10, Ireland},postcodesep={}}

@@

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

Uptake of cycling, the main topic of this paper, should be seen in this
broader context of transport decarbonisation \citep{brand2020}. Although
cycling uptake appears on the surface to only relate to the `shift' part
of the ASI framework, closer consideration of the knock-on impacts of
cycling uptake shows that it can also help avoid unnecessary trips
{[}citation needed, any ideas Hussein?{]} . The rapid uptake of highly
efficient e-bikes can also be seen as an improvement on most electric
vehicles, which are too heavy and expensive to be a sustainable
alternative and could in fact delay the transition away from car
dependency {[}citation needed{]}.

@@

In this context, TII commissioned the CRUSE project which is\ldots{}

The rest of paper is structured as follows\ldots{}
